---
title: "ODD_Retail_Sales_201608"
author: "Kadir Kemal Dursun"
date: "10/30/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(magrittr)
library(tidyverse)
```

## Download Raw Data

The raw data (excel file) has been uploaded to my github repository. First we download that file and put the data in a temp file. Then we can read that excel file into R and finally we will remove the temp file.

```{r}

# Create a temporary file
tmp<-tempfile(fileext=".xlsx")
# Download file from repository to the temp file
download.file("https://github.com/MEF-BDA503/pj18-KadirKemal/blob/master/Week2/Odd_Retail_Sales_2017_08.xlsx?raw=true",destfile=tmp)
# Read that excel file using readxl package's read_excel function. You might need to adjust the parameters (skip, col_names) according to your raw file's format.
raw_data<-readxl::read_excel(tmp,skip=7,col_names=FALSE)
# Remove the temp file
file.remove(tmp)

```

## See The Raw Data

You can also embed plots, for example:

```{r}
# Let's see our raw data
head(raw_data)
```

## Remove Total Colums and Last Two Rows
```{r}

lastRowIndex = length(raw_data$X__1)-2
raw_data = raw_data[1:lastRowIndex, c(1:10)]

# Let's see our raw data
head(raw_data)
tail(raw_data)
```

## Set the column titles
```{r}
colnames(raw_data) <- c("brand_name","auto_dom","auto_imp","auto_total","comm_dom","comm_imp","comm_total","total_dom","total_imp","total_total")

head(raw_data)
```

## Replace NA values With 0
```{r}

raw_data[is.na(raw_data)] = 0
head(raw_data)

car_data_agu_16 = raw_data
car_data_agu_16 %>% mutate(year=2016,month=8)
```


## Save Data
```{r}
saveRDS(car_data_agu_16,file="~/Documents/GitHub/pj18-KadirKemal/Week2/odd_car_sales_data_agu_16.rds")
```

## Find the lines that auto_total and comm_total is bigger than 0
```{r}
car_data_agu_16[car_data_agu_16$auto_total > 0 & car_data_agu_16$comm_total > 0,c(1,4,7)]
```

## Find average of auto_total
```{r}
mean(car_data_agu_16$auto_total)
```

## Summary Data
```{r}
summary(car_data_agu_16)
```

